---
title: "Strava Suffer Score"
author: "Saryu Onishi"
date: "`2023-04`"
output:
  xaringan::moon_reader:
    css: ['default', 'metropolis', 'metropolis-fonts','sp23.css']
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
    seal: false
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
class: title-slide   
<br><br>
# Exploring Strava's Suffer Score
## ECON 5252 Final Project
### Saryu Onishi 

---
# Introduction
## Strava
This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
## Suffer score
When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

---

# Data
## Strava API
- Bullet 1
- Bullet 2
- Bullet 3

---

# Methods

```{r cars, echo = TRUE}
summary(cars)
```

---

# Findings
.pull-left[
## sub-title
- heteroscedasticity
]

.pull-right[
```{r}
ggplot(plot_data, aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "loess") +
  labs(x = "Suffer Score", y = "Residuals")
```
]

---
# So what?

